% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org

% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca

% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com

% (c) 2011 Scott Clark <sc932@cornell.edu> http://cam.cornell.edu/~sc932
%

%(c) 2011 Anthony Kosednar <me@anthonykosednar.com> http://anthonykosednar.com/

%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

\newlength{\outerbordwidth}

\pagestyle{empty}

\raggedbottom

\raggedright

\usepackage[svgnames]{xcolor}

\usepackage{framed}

\usepackage{tocloft}

%-----------------------------------------------------------

%Edit these values as you see fit

\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars

\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)

\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars

%-----------------------------------------------------------

%Margin setup

\setlength{\evensidemargin}{-0.25in}

\setlength{\headheight}{-0.25in}

\setlength{\headsep}{0in}

\setlength{\oddsidemargin}{-0.25in}

\setlength{\paperheight}{11in}

\setlength{\paperwidth}{8.5in}

\setlength{\tabcolsep}{0in}

\setlength{\textheight}{9.75in}

\setlength{\textwidth}{7in}

\setlength{\topmargin}{-0.3in}

\setlength{\topskip}{0in}

\setlength{\voffset}{0.1in}

%-----------------------------------------------------------

%Custom commands

\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}

\newcommand{\resheading}[1]{\vspace{8pt}

  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}

    \begin{shaded}

\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}

    \end{shaded}

  }\vspace{-5pt}

}

\newcommand{\ressubheading}[4]{

\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}

		\textbf{#1} & #2 \\

		\textit{#3} & \textit{#4} \\

\end{tabular*}\vspace{-6pt}}

%-----------------------------------------------------------

\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}

\textbf{\Large Anthony Kosednar} & \textbf{\today} \\

{Website Developer} & {akosednar@asu.edu} \\

2835 East Park Ave., Gilbert, AZ 85234 & http://anthonykosednar.com/

\end{tabular*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Education}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item

	\ressubheading{Arizona State University}{Tempe, AZ}{Ira A. Fulton Schools of Engineering}{Aug. 2012 - May 2016 (projected)}

	\begin{itemize}

		\resitem{Astronautical Aerospace Engineering}

	\end{itemize}
\item

	\ressubheading{Chandler Preparatory Academy}{Chandler, AZ}{High School Education}{Aug. 2008 - May 2012}

	\begin{itemize}

		\resitem{4 years Honors Humane Letters and French}

		\resitem{2 years Honors Calculus and Physics}

		\resitem{1 year Honors Geometry, Algebra, Chemistry, and Biology}

		\resitem{2 Semesters Music, Drama, Art, and Poetry}
		
		\resitem{Senior Thesis}

	\end{itemize}

\item

	\ressubheading{Arizona State University}{Tempe,AZ}{School of Mathematical and Statistical Sciences}{Aug. 2010 - Present}
	\ressubheading{Arizona State University}{Tempe, AZ}{School of Mathematical and Statistical Sciences}{Aug. 2010 - April 2012}

	\begin{itemize}

		\resitem{High School Program (Math Circles), Non-Credit Granting}

		\resitem{Number Theory, Field Theory, Cryptography, and Statistics}

	\end{itemize}
	
\item

	\ressubheading{Rio Salado College}{Phoenix, AZ}{French Language Study}{June 2011 - Aug. 2011}

	\begin{itemize}

		\resitem{French 102}

	\end{itemize}

\end{itemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Skills}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item {\bf Development:} PHP, HTML, CSS, JavaScript, AutoIt, Python

\item {\bf Computer Science:} Data Mining, Operating Systems

\item Discovering and implementing new ideas.

\item I can readily learn and adapt to a new discipline, area or environment and start producing real results quickly.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Work Experience}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item

	\ressubheading{Arizona State University}{Tempe, AZ}{Contracted Website Developer}{Aug. 2011 - Oct. 2011}

	\begin{itemize}

		\resitem{Maintained \texttt{Windows IIS Server} and \texttt{Linux LAMP Stack}}

    		\resitem{Developed, and Maintained CMS solutions for Departments}

	\end{itemize}

\item

	\ressubheading{Lockerhub}{Gilbert, AZ}{Founder}{Aug. 2009 - Present}

	\begin{itemize}

		\resitem{Developed Websites and Applications for a range of Clients}

  		 \resitem{System Administrator for a Network of Servers running  \texttt{Citrix XenServer} }

	\end{itemize}

\item 

	\ressubheading{TechnoKOZ}{Gilbert, AZ}{Computer Technician}{July 2008 - Present}

	\begin{itemize}

		\resitem{Installed, repaired, maintained, and upgraded servers, desktop and notebook computers}

 		 \resitem{Installed and maintained network equipment}

	\end{itemize}

\item

	\ressubheading{Cybermark International Inc.}{Phoenix, AZ}{Search Engine Optimization Engineer}{May 2008 - Aug. 2008}

	\begin{itemize}

		\resitem{Preformed Back-link Campaigning for Clients}
		\resitem{Preformed Social Media Campaigning for Clients}

	\end{itemize}
	
\end{itemize}

\end{document}